%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{bibentry}
\usepackage{natbib}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Yanwen Xu} % Your name
\address{Santa Cruz, CA 95060 \\ +1 (507) 858-5167} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{xu\_yanwen@aol.com \\ yxu-k6mlx.github.io} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\nobibliography*
\begin{rSection}{Summary}
I am Yanwen Xu, I have recently finished my master's degree at University of California, Santa Cruz in Computer Science and Engineering. Through my studies, I have gained over 4 years of hand-on experience working with various AI/ML models built on top of popular machine learning libraries such as TensorFlow or PyTorch. I have built and deployed web based applications as both a middleware and API developer, and a back-end developer. In addition, I have achieved significant successes in my communications skills, thanks to my great friend and mentor, Gary Young, a local poet in Santa Cruz. Together, we have published over ten pieces on various literature journals, as well as a jointly authored book in poetry. 
\end{rSection}

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
{\bf University of California, Santa Cruz}\\
Master of Science in Computer Science\hfill {\em 09/2022 - 06/2024}
\\ Bachelor of Science in Computer Science\hfill {\em 09/2018 - 06/2022}  
%--copy and paste this region  if you need more--

\end{rSection}
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}
%--copy and paste this region  if you need more--
{\bf Tech4Good Lab}{, Member} \hfill {\em 06/2023 - 10/2023}\\
Planned and programmed experiments as a member of the AI Economist team. \\
{\bf AIEA}{, Graduate Student Researcher} \hfill {\em 01/2024 - 06/2024}\\
Developed a visualizer component in lab's intelligent auto-grader project used for an AI algorithm class. 
%--copy and paste this region  if you need more--
\end{rSection}
%--------------------------------------------------------------------------------
%    PROJECTS
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
%--copy and paste this region  if you need more--
{\bf world.explore()}{, Participant, Supervisor: Prof. Daniel Goodman Shapiro} \hfill {\em 09/2021 - 12/2021}\\
Built a web-based interactive social game client using HTML and JavaScript.\\
Used API links to websites and implemented real-time social and problem-solving functions.\\
Built a Python3 program using Convolutional Neural Networks to determine whether a photo location matches the
studied location in a database based on an uploaded photo, and linked it to a front-end web client.

{\bf Intro to ML}{, Participant, Supervisor: Assistant Prof. Yang Liu} \hfill {\em 09/2021 - 12/2021}\\
Involved in a machine learning project using the Sklearn module in Python3. \\
Utilized the Pandas module to process random data in JSON format and predicted the target data. \\
Conducted the data visualization using Python3’s library. \\
Obtained a widely used numerical information prediction AI, which can be applied to market trend prediction and
enterprise intelligent resource allocation. 

{\bf High Street Online Project}{, Participant, Supervisor: Prof. Luca de Alfaro} \hfill {\em 04/2021 - 06/2021}\\
Carried out the website framework and user interaction function design. \\
Utilized JQuery to design database structure. \\
Employed HTML, CSS, and Vue.js for front-end design and Py4Web for back-end support. 

{\bf AI Graph Search 2.0}{, Developer, Supervisor: Prof. Leilani Gilpin} \hfill {\em 06/2024 - Present}\\
Adopted an open source Python software, AI Graph Search, and developed the software further. \\
The modified software can take in user written AI algorithms and visualize said algorithm in
node tree representation. 

%--copy and paste this region  if you need more--
\end{rSection}
%--------------------------------------------------------------------------------
%    ACTIVITIES
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Work Experiences}
%--copy and paste this region  if you need more--
{\bf SkyLeap Group}{, Member and Communications Lead} \hfill {\em 06/2012 - Present}\\
Engaged in Indie software/game localization in Mandarin Chinese context. \\
Responsible for back-end text file manipulation and software/game localization-related testing.\\
Onboard teams that published simulation software/games such as 911 Operator, Car Mechanic Simulator 2015, Car Mechanic Simulator 2018, X-Plane 11, etc. on the Steam platform.\\
%--copy and paste this region  if you need more--
\end{rSection}
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\end{document}----------------------------

